---
title: "K-means Example"
author: "Dan Veltri"
date: "2/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

We will be importing Fishers Iris dataset. It contains 50 samples each for three different Iris spp. (rows)

* Four measurements/features (cols) per flower
  + sepal length
  + sepal width
  + petal length
  + petal width
* Species Class is the final column (setosa, versicolor, virginica)


```{r iris-data}
data('iris')
head(iris) # see what it looks like
iris.x <- iris[,1:4] # measurements
iris.y <- iris[,5] # our response labels

summary(iris)
```


## Perform k-Means Clusting

The `kmeans` function comes with the base R stats package. We give it the dataframe, the number of `centers` (** k **), `nstart` the number of times to re-run the procedure, and the algorithm type. Here we use MacQueen but others are available, see: `help(kmeans)`. Inspect the output of the function!

```{r kmeans}

set.seed(12345)
iris.kmeans <- kmeans(iris.x, centers=3, nstart = 25, algorithm="MacQueen")

print(iris.kmeans)

table(ACTUAL=iris.y, KMeansClusts=iris.kmeans$cluster)

```

## Challenge Questions
What cluster number appears to have been assigned to each iris species? How could you use these clusters to help visualize them? 
