---
title: "RandomForest Example"
author: "Dan Veltri"
date: "2/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list.of.packages <- c("randomForest")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="http://cran.r-project.org")

library(randomForest) # provides basic randomForest - the package "ranger" is also good!
```

# Example with Iris Data 

```{r iris-data}
data('iris')
attach(iris)

# randomly get indexes for half of the data
train_idx = sample(seq(1,nrow(iris)),round(nrow(iris)/2))
iris.train = iris[train_idx,]
iris.test = iris[-train_idx,]


# Apply randomForest with 100 trees - set importance = T to see feature importance
iris.rf100 = randomForest(Species ~ ., data = iris.train, ntree=100, importance=TRUE)

# See training performance
iris.rf100

# Make predictions on Test Data
preds = predict(iris.rf100, newdata=iris.test)

# See prediction results table
table(Actual=iris.test$Species, RF_Preds=preds)

# How important was each feature for prediction?
iris.rf100$importance
